\Large \bf Uncovering Distributed Storage System Bugs during\\Testing (not in Production!)

### 2015-09-21 evaluation.tex
Edits to MigratingTable evaluation.
Specifically, revise the discussion of the 4 bugs the default test
harness did not find.

Developing the Live Migration Table and its \psharp test harness took about five weeks. The test harness was developed in parallel with the actual system. This is in contrast with the other two case studies discussed in this paper, where the modeling activity occurred independently and at a later stage of the development process.

@@

Using \psharp we managed to uncover 12 serious bugs in our case studies \PDComment{update for Fabric}. As discussed earlier in the paper, these bugs were hard to find with traditional testing techniques, but \psharp managed to uncover them and reproduce them in a small setting. According to the developers, the traces of \psharp were useful, as it allowed them to understand the source of the bug and fix it in a timely manner. After the developers fixed all the discovered bugs, we optionally reintroduced them one-by-one to evaluate the effectiveness of different \psharp systematic testing strategies in finding these bugs.

Table~\ref{tab:testing} presents the results from running the \psharp systematic testing engine on each case study with a re-introduced bug using the random and PCT schedulers. We chose to use controlled random scheduling, because it has proven to be efficient for finding concurrency bugs~\cite{thomson2014sct, deligiannis2015psharp}. The CS column shows which case study corresponds to each bug: 1 is for the Azure Storage vNext; and 2 is for the Live Migration Table. \PDComment{update with 3 for Fabric}

@@

For the MigratingTable case study, the first seven bugs in Table~\ref{tab:testing} were discovered using a \psharp test harness based on nondeterministically generated, but controlled by \psharp, input history. For each of these found bugs, we manually reviewed one of the bug traces to confirm if it reflected the expected bug. The remaining four bugs (denoted with $\diamond$) were not caught with our default test harness in the 100,000 iterations (a process that required less than 30 minutes). We believe this is due to unlucky random choices of inputs and schedules by the \psharp testing engine. We wrote a custom \psharp test harness for each of these bugs, which allowed \psharp to quickly reproduce them. The design of these custom harnesses was influenced by the knowledge of these bugs; our objective here was to simply see if \psharp can reproduce these known bugs.

>>>>

Developing MigratingTable and its \psharp test harness took about five weeks. The test harness was developed in parallel with the actual system. This is in contrast with the other two case studies discussed in this paper, where the modeling activity occurred independently and at a later stage of the development process.

@@

Using \psharp we managed to uncover 8 serious bugs in our case studies \PDComment{update for Fabric}. As discussed earlier in the paper, these bugs were hard to find with traditional testing techniques, but \psharp managed to uncover them and reproduce them in a small setting. According to the developers, the traces of \psharp were useful, as it allowed them to understand the source of the bug and fix it in a timely manner. After the developers fixed all the discovered bugs, we optionally reintroduced them one-by-one to evaluate the effectiveness of different \psharp systematic testing strategies in finding these bugs.

Table~\ref{tab:testing} presents the results from running the \psharp systematic testing engine on each case study with a re-introduced bug using the random and PCT schedulers. We chose to use controlled random scheduling, because it has proven to be efficient for finding concurrency bugs~\cite{thomson2014sct, deligiannis2015psharp}. The CS column shows which case study corresponds to each bug: 1 is for the Azure Storage vNext; and 2 is for MigratingTable. \PDComment{update with 3 for Fabric}

@@

For the MigratingTable case study, we evaluated the \psharp test harness of \S\ref{sec:cases:migration} on 11 ``bugs'', including 8 that actually occurred in development and 3 other code changes that we deemed interesting ways of making the code incorrect. The test found seven of the bugs, which are listed first in Table~\ref{tab:testing}. The remaining four bugs (denoted with $\diamond$) were not caught with our default test harness in the 100,000 iterations (a process that required less than 30 minutes). We believe this is because the inputs and schedules that trigger them are too rare in our distribution. To confirm this, we wrote a custom test case for each bug with a specific input that triggers it and were able to quickly reproduce the bugs, as shown. This method is useful for regression testing, but one could not use it during development with no prior knowledge about the bugs.
